A full approximation storage multilevel method \\ for nonlinear variational inequalities

### 2023-06-24 paper/fascd.tex
plan to include weak scaling in SIA results

Algorithms \ref{alg:fascd} and \ref{alg:fascd-fcycle} were implemented in Python using the Firedrake library \cite{Rathgeberetal2016}.  In this Section we show numerical results corresponding to several VI examples from Section \ref{sec:vi}, with a focus on the scaling of FASCD iterations as the mesh resolution increases.  Our essential observation is that, with strong $O(m_J)$ smoothers on each level, each V-cycle dramatically reduces the residual norm, and generally a couple of F-cycles solves the problem down to discretization error.

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/drape.py and edplay/resultsdrape.sh|txt
% note mcoarse=4, rtol=1e-6, atol=1e-12
% smoother is vinewtonrsls + 3 x (cg + icc), coarse solver is vinewtonrsls + lu
\begin{table}[ht]
\begin{tabular}{lr@{\hskip 7mm}cccccc}
\multirow{2}{*}{\emph{levels}} & \multirow{2}{*}{$m_J$} & \multicolumn{3}{c}{\,\emph{ball}} & \multicolumn{3}{c}{\,\emph{spiral}} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8}
   &          & V-cycle & F-cycle & RS only & V-cycle & F-cycle & RS only \\ \cmidrule{1-8}
 1 &    $5^2$ &  1 &  1 &  1  &  1 &  1 &  1 \\
 2 &    $9^2$ &  2 &  1 &  2  &  2 &  1 &  2 \\
 3 &   $17^2$ &  2 &  2 &  3  &  3 &  2 &  4 \\
 4 &   $33^2$ &  3 &  2 &  6  &  3 &  2 &  7 \\
 5 &   $65^2$ &  3 &  2 &  8  &  4 &  3 &  9 \\
 6 &  $129^2$ &  4 &  2 & 17  &  4 &  3 & 16 \\
 7 &  $257^2$ &  4 &  2 & 33  &  4 &  3 & 27 \\
 8 &  $513^2$ &  5 &  2 & 65  &  5 &  3 & 48 \\
 9 & $1025^2$ &  5 &  2 & \XX &  5 &  3 & \XX \\
10 & $2049^2$ &  5 &  2 & \XX &  5 &  3 & \XX
\end{tabular}
\bigskip
\caption{Iterations for FASCD V-cycle and F-cycle algorithms in Example \ref{ex:results:classical}.  Smoother-only runs marked \XX\xspace were not attempted.}
\label{tab:results:classical}
\end{table}

@@

% for Tables \ref{tab:results:fastplap1d} and \ref{tab:results:degenerateplap1d},
% see git@bitbucket.org:pefarrell/fascd.git: examples/plap1d.py and edplay/resultsplap1d.sh|txt

@@

\begin{example}   \label{ex:results:sia}
FIXME results for SIA obstacle problem, Example \ref{ex:sia}
\end{example}

@@

FIXME

FIXME the observation that up-smoothing is more efficient; this observation seems to be new; compare the comments on V(1,0) and V(1,1) cycles in \cite{GraeserKornhuber2009,Tai2003}

>>>>

Algorithms \ref{alg:fascd} and \ref{alg:fascd-fcycle} were implemented in Python using the Firedrake library \cite{Rathgeberetal2016}.  In this Section we show numerical results corresponding to several VI examples from Section \ref{sec:vi}, with a focus on the scaling of FASCD iterations as the mesh resolution increases.  Assuming strong $O(m_J)$ smoothers on each level, as illustrated in the Examples, our essential observations are that each V-cycle dramatically reduces the residual norm, and that a couple of F-cycles solves the problem down to discretization error.

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/drape.py and edplay/results/drape.sh|txt
% note mcoarse=4, rtol=1e-6, atol=1e-12
% smoother is vinewtonrsls + 3 x (cg + icc), coarse solver is vinewtonrsls + lu
\begin{table}[ht]
\begin{tabular}{lr@{\hskip 7mm}cccccc}
\multirow{2}{*}{\emph{levels}} & \multirow{2}{*}{$m_J$} & \multicolumn{3}{c}{\,\emph{ball}} & \multicolumn{3}{c}{\,\emph{spiral}} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8}
   &          & V-cycle & F-cycle & RS only & V-cycle & F-cycle & RS only \\ \cmidrule{1-8}
 1 &    $5^2$ &  1 &  1 &  1  &  1 &  1 &  1 \\
 2 &    $9^2$ &  2 &  1 &  2  &  2 &  1 &  2 \\
 3 &   $17^2$ &  2 &  2 &  3  &  3 &  2 &  4 \\
 4 &   $33^2$ &  3 &  2 &  6  &  3 &  2 &  7 \\
 5 &   $65^2$ &  3 &  2 &  8  &  4 &  3 &  9 \\
 6 &  $129^2$ &  4 &  2 & 17  &  4 &  3 & 16 \\
 7 &  $257^2$ &  4 &  2 & 33  &  4 &  3 & 27 \\
 8 &  $513^2$ &  5 &  2 & 65  &  5 &  3 & 48 \\
 9 & $1025^2$ &  5 &  2 & \XX &  5 &  3 & \XX \\
10 & $2049^2$ &  5 &  2 & \XX &  5 &  3 & \XX
\end{tabular}
\bigskip
\caption{Iterations for FASCD V-cycle and F-cycle algorithms in Example \ref{ex:results:classical}.  Smoother-only runs marked \XX\xspace were not attempted.}
\label{tab:results:classical}
\end{table}

@@

% for Tables \ref{tab:results:fastplap1d} and \ref{tab:results:degenerateplap1d},
% see git@bitbucket.org:pefarrell/fascd.git: examples/plap1d.py and edplay/results/plap1d.sh|txt

@@

Solvers implemented in Firedrake apply parallel solvers from the PETSc library \cite{Balayetal2023}.  All of the above Examples, which were run in serial so as to fix the smoother,\footnote{The precise action of $O(m_j)$ work parallel smoothers depends on the number of processes \cite[for example]{Bueler2021}.} can in fact be run efficiently in parallel.  We start the next example with a demonstration of parallel weak scaling, and then explore the performance of the FASCD method up to memory-limited resolutions.

\begin{example}   \label{ex:results:sia}
FIXME results for SIA obstacle problem, Example \ref{ex:sia}; start with weak scaling; show Paraview-generated Figure
\end{example}

@@

FIXME the observation that up-smoothing is more efficient seems to be new; compare the comments on V(1,0) and V(1,1) cycles in \cite{GraeserKornhuber2009,Tai2003}

FIXME smoother could be AMG
